\racets: Policy{-}Agnostic Programming in Racket

### 2018-07-24 paper/paper.tex
adding paragraph on faceted interactions

\paragraph*{}

>>>>

\paragraph*{Module Interactions in \racets}

There is a wealth of existing Racket code we might like to incorporate
into \racets programs. For example, our case study uses the
\texttt{web-server} framework for building web applications. However,
in general, we believe that interacting with code not written using
faceted execution is a challenging open problem, and we do not know of any
principled solutions in the literature.

One immediate problem in \racets is how to pass functions from \racets
to plain Racket code. For example, the \texttt{web-server} framework
is written in Racket, and does not know how to call tagged closures
from \racets. As a stopgap, we added an \code{ext-lambda} form to
\racets. This form allows creating a Racket-style lambda in Racets
that will be used by functions in other modules, necessary for the
implementation of our case study.

We plan to explore interactions with unfaceted code more in the
future, and believe it will an exciting direction. For example, once
execution escapes \racets, we have no guarantee that the privacy
policy won't be violated. One solution may be to implicitly perform an
\code{obs} based on the current \rmth{pc} at points where \racets
interacts with unfaceted modules. But we do not fully understand the
ramifications or ergonomics of this choice, and suspect there may be a
wide array of design choices to handle these module interactions
including security type systems and blame (to track which module
violated the privacy policy).
